<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{a) State Unemployment Data}
-->

US State Unemployment Data
========================================================

### Data

This package contains a data.frame called `df_state_unemployment` which contains unemployment data on US States from 2000-2014. The data is annualized, which means that there is one data point per State per year:

```{r}
library(rUnemploymentData)

data(df_state_unemployment)
?df_state_unemployment

head(df_state_unemployment)
```

The data was scraped from the US Bureau of Labor Statistics (BLS) Local Area Unemployment Statistics (LAUS) webpage on January 2, 2014 (http://www.bls.gov/lau/). For the purposes of reproducbility, the scripts which scraped the data also ship with this package - see function `build_state_df` for details.

### Visualization - Boxplot

The easiest way to visualize the entire dataset is with a boxplot. 

```{r}
?boxplot
boxplot(df_state_unemployment[, -1],
        main="USA State Unemployment Data",
        xlab="Year",
        ylab="Percent Unemployment")
```

This visualization shows you, by year, the distribution of the unemployment rate in each state.  For example, the recession that began in 2009 is very clear in this graph. 

### Visualization - Choropleth Map

This package also comes with a function to create choropleth maps of the data:

```{r}
?state_unemployment_choropleth
state_unemployment_choropleth(year=2013)
```

Choropleth maps are useful for understanding the geographic distribution of values. For example, in this map it is clear that the lowest unemployment rates were in the northern central states.

### Visualization - Animated Choropleths

A third option for visualizing the data is with an animated choropleth map:

```{r}
?animated_state_unemployment_choropleth
# animated_state_unemployment_choropleth()
```

This function is commented out in the above example because the resulting image cannot render inside a vignette. If you are interested in this visualization, then please type the command locally.